\documentclass[11pt,oneside,DIV=calc,parskip=off]{scrarticle} %DIV=calc defaults to DIV=8

%%% FONT AND TYPESETTING %%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{fontspec}
	\setmainfont[
		Ligatures={TeX,Common}, 
		Numbers={Proportional},
		BoldFont = * Semibold,
		ItalicFont = * Italic,
		BoldItalicFont = * Semibold Italic,
		SmallCapsFeatures = {BoldFont= * Semibold, BoldItalicFont= * Semibold Italic},
		]{Libertinus Serif}

\usepackage{microtype}% Better typographical adjustments
\usepackage{fontawesome5}% Cool icons
\usepackage{pbox}% Boxes that automatically fit contents

%Reduce amount of hyphenation
\lefthyphenmin=4
\righthyphenmin=4

\usepackage{graphics}

%%% HEADERS AND FOOTERS %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{titling}
\usepackage[manualmark,headsepline]{scrlayer-scrpage}
	%With one-sided document, all pages are right-hand pages: 
	%i = inner = left, o = outer = right
%	\ihead{William Johnston}\chead{}\ohead{Curriculum Vitae}% I prefer this one
	\ihead{Curriculum Vitae}\chead{}\ohead{William Johnston}% 
	\ifoot{}\cfoot*{\pagemark}\ofoot*{\scriptsize Last updated: \today}% I prefer this one

%%% LINKS AND REFERENCES %%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{hyperref}
	\hypersetup{colorlinks=true,linkcolor=cyan,filecolor=cyan,urlcolor=cyan}
	\urlstyle{same}

%%% SPACING %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Remove paragraph indent
\setlength{\parindent}{0pt}

% Create and set custom column widths
\newlength{\leftcolwidth}
\newlength{\mycolspace}
\newlength{\rightcolwidth}
\setlength{\leftcolwidth}{7.4em}
\setlength{\mycolspace}{1em}
\setlength{\rightcolwidth}{\dimexpr(\linewidth-8.4em)\relax}

% Create and set a standard unit of vertical spacing
\newlength{\basicverticalspace}
\setlength{\basicverticalspace}{0.66\bigskipamount}

% Create and set custom spacing before and after CV items
\newlength{\spacingbefore}
\newlength{\spacingafter}
\setlength{\spacingbefore}{0\basicverticalspace}
\setlength{\spacingafter}{1\basicverticalspace}

% Spread out items vertically over full page
%\AtBeginDocument{\flushbottom}
	
% Set hanging indent for right-hand column entries
\newcommand{\hang}{\hangindent=0.75em\hangafter=1}

%%% SECTION HEADINGS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%Fonts for headings:
\addtokomafont{section}{\Large\rmfamily\bfseries\scshape}
\addtokomafont{subsection}{\large\rmfamily\mdseries\scshape}
\addtokomafont{subsubsection}{\rmfamily\mdseries\itshape}
\addtokomafont{paragraph}{\rmfamily\mdseries\scshape}
%\addtokomafont{subparagraph}{\rmfamily\mdseries\scshape}

%Remove all section numbers
\setcounter{secnumdepth}{0}

%Run-in and indented headings
\RedeclareSectionCommands[runin=false]{section,subsection,subsubsection}
\RedeclareSectionCommands[runin=true]{paragraph,subparagraph}
\RedeclareSectionCommands[indent=1.5em]{subsubsection,subparagraph}

%Spacing before/after headings:
\RedeclareSectionCommand[%
	beforeskip=1.5\basicverticalspace,
	afterskip=1\basicverticalspace,
	]{section}
\RedeclareSectionCommand[%
	beforeskip=1.1\basicverticalspace,
	afterskip=1\basicverticalspace,
	]{subsection}
\RedeclareSectionCommand[%
	beforeskip=0.75\basicverticalspace,
	afterskip=0.75\basicverticalspace,
	]{subsubsection}
\RedeclareSectionCommand[%
	beforeskip=0\basicverticalspace,
	afterskip=0.5em,
	]{paragraph}
\RedeclareSectionCommand[%
	beforeskip=0\basicverticalspace,
	afterskip=0.5em,
	]{subparagraph}


%%% MACROS FOR CV ITEMS %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Basic formatting for one-column entries
\newcommand{\myonecol}[1]{%
	\vspace{\spacingbefore}%
	\begin{minipage}[t]{\linewidth}%
		\strut#1%
	\end{minipage}%
	\vspace{\spacingafter}\par%
	}

%Basic formatting for two-column entries	
\newcommand{\mytwocol}[2]{%
	\vspace{\spacingbefore}%
	\begin{minipage}[t]{\leftcolwidth}%
		\strut#1%
	\end{minipage}%
	\hspace{\mycolspace}%
	\begin{minipage}[t]{\rightcolwidth}%
		\strut#2%
	\end{minipage}%
	\vspace{\spacingafter}\par%	
	}

%Formatting for publications
\newcommand{\pub}[1]{%
	\myonecol{#1}%
	}

%Formatting for talks
\newcommand{\talk}[1]{%
	\myonecol{#1}%
	}

%Formatting for generic undated items
\newcommand{\undated}[1]{%
	\myonecol{#1}%
	}

%Formatting for dated CV items
\newcommand{\cvline}[2]{%
	\mytwocol{#1}{#2}%
	}
	
%Formatting for notes (with smaller text)
\newcommand{\noteline}[2]{%
	\vspace{-.9\spacingafter}%
	{\footnotesize\mytwocol{#1}{\everypar{\hang}#2}}%
	}
	
%%% MACROS FOR CONTACT INFO + ICONS %%%%%%%%%%%%%%
\newcommand{\addfaicon}[2]{% #1 = faicon, #2 = text
	\raisebox{-1pt}{\small#1}\enspace#2%
	}

\newcommand{\email}[1]{\addfaicon{\faEnvelope}{\href{mailto:#1}{#1}}}
\newcommand{\splitemail}[2]{\addfaicon{\faEnvelope}{\href{mailto:#1#2}{#1}\\\null\qquad{\href{mailto:#1#2}{#2}}}}
\newcommand{\website}[1]{\addfaicon{\faGlobe}{\href{https://#1}{#1}}}
\newcommand{\github}[1]{\addfaicon{\faGithub}{\href{https://#1}{#1}}}
\newcommand{\phone}[1]{\addfaicon{\faPhone}{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\thispagestyle{plain}

\begin{center}
{\huge{William Johnston}}\\
\vspace{\baselineskip}
\textsc{\Large Curriculum Vitae}\\
\end{center}\par

\vspace{2\basicverticalspace}

%%% CONTACT INFO %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pbox[t]{0.5\linewidth}{	
	Département de linguistique\\
	Université du Québec à Montréal\\
	C.P. 8888, Succ.\ Centre-Ville\\
	Montréal, QC H3C 3P8 Canada
	}
\hfill
\pbox[t]{0.5\linewidth}{
	\website{williamjohnston.github.io}\\
	\splitemail{johnston.william\_christopher}{@courrier.uqam.ca}\\
%	\github{}\\
%	\phone{}
	}

\vspace{2\basicverticalspace}

%%% EDUCATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
\cvline{Ph.D, 2024}{Linguistics, McGill University} 
	\noteline{}{Dissertation: \textit{Event structure and serial verbs in Hmong.}\par Supervisory committee: Jessica Coon and Luis Alonso-Ovalle (co-supervisors), Junko Shimoyama, and Lisa Travis. External examiner: Peter Svenonius.}
\cvline{B.A., 2013}{Linguistics, Carleton College (Northfield, MN)}

%%% PROFESSIONAL %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Employment}

\cvline{2024--present}{Postdoctoral researcher\\Département de linguistique, Université du Québec à Montréal}
	\noteline{}{Fonds de recherche du Québec - Société et culture (FRQSC) Postdoctoral Fellowship, supervised by Richard Compton.}

\cvline{Fall 2024}{Course Lecturer\\Département de linguistique, Université du Québec à Montréal}

\cvline{Winter 2023}{Course Lecturer\\Department of Linguistics, McGill University}

\cvline{Winter 2021}{Course Lecturer\\Department of Linguistics,McGill University}


%%% RESEARCH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Research}

\subsection{Grants \& Fellowships}

\pub{Fonds de recherche du Québec (FRQ) Postdoctoral Fellowship, 2024--2026. Project: \textit{Les catégories syntaxiques en hmong blanc: implications pour la théorie linguistique et l'enseignement des langues | Syntactic categories in White Hmong: Implications for linguistic theory and language education}, \$90,000 CAD.}

\subsection{Journal Articles}

\pub{\textbf{Johnston, William.} (2023). ``Pair-list answers to questions with plural definites.'' \textit{Semantics and Pragmatics} 16(2). \href{https://doi.org/10.3765/sp.16.2}{https://doi.org/10.3765/sp.16.2}}

%\subsection{Book Chapters}

\subsection{Conference Proceedings}

\pub{\textbf{Johnston, William.} (Forthcoming). ``Decomposing Path: Deprepositional verbs in White Hmong'' In: \textit{Proceedings of the 42\textsuperscript{nd} West Coast Conference on Formal Linguistics}. %Ed.\ by
}
\pub{\textbf{Johnston, William.} (Forthcoming). ``Culmination entailments in V and P: Evidence from White Hmong.'' In: \textit{Proceedings of the 41\textsuperscript{st} West Coast Conference on Formal Linguistics}. Ed.\ by Yağmur Kiper, Larry Lyu, Richard Wang, and Niko Webster. Somerville, MA: Cascadilla Press.}
\pub{\textbf{Johnston, William.} (2024). ``Two diagnostics for preposition-hood: Decomposing Path in White Hmong.'' In: \emph{Proceedings of the 14th Generative Linguistics in the Old World in Asia (GLOW in Asia XIV) 2024.} Ed.\ by Xiangyu Li, Zetao Xu, Yuqiao Du, Zhuo Chen, Chenghao Hu, Zhongyang Yu, and Victor Junnan Pan.}
\pub{\textbf{Johnston, William.} (2022). ``Nonspecific promises: The Intensional Restitution Effect.'' In: \textit{Proceedings of Sinn und Bedeutung 26}. Ed.\ by Daniel Gutzmann and Sophie Repp. pp.\ 483--502. University of Cologne.}
\pub{\textbf{Johnston, William.} (2019). ``Pair-list questions from dependent plurals.'' In: \textit{Proceedings of the 22\textsuperscript{nd} Amsterdam Colloquium}. Ed.\ by Julian J.\ Schl\"oder, Dean McHugh, and Floris Roelofsen. pp.\ 201--210. Amsterdam: ILLC.}

%\subsection{Book Reviews}

%\subsection{Edited Volumes}

\subsection{Manuscripts}
\pub{\textbf{Johnston, William.} (In revision). ``Paths across worlds: the presupposition of back in intensional contexts.'' %[\href{}{lingbuzz}]
} 

\pub{\textbf{Johnston, William.} (In revision). ``Causation and serialization in White Hmong.''} %[\href{https://ling.auf.net/lingbuzz/007585}{lingbuzz}]

\subsection{Invited Talks}
\talk{``Causation and serialization in Hmong.'' \textit{Converging on Causal Ontology Analyses}. Centre national de la recherche scientifique (CNRS), Paris. October 11, 2024.}

\talk{``Path in Hmong: The structure of directional PPs.'' \textit{Annual Conference of the Canadian Linguistic Association}. Carleton University, Ottawa. June 19, 2024.}

\talk{``The verb phrase in Hmong: Serialization and event structure.'' \textit{University of Minnesota Linguistics Colloquium Series}. November 11, 2022.}

%\subsection{Invited Commentaries}

\subsection{Refereed Conference Presentations}
\subsubsection{Talks Delivered:}
%\talk{``Parts of speech in Hmong.'' \textit{6\textsuperscript{th} Hmong Studies Consortium International Conference}, Merced College, Merced, CA. November 2, 2024.}
%note ad-hoc spacing:
\talk{``Clausal Complementation, Finiteness and Object Control in Hmong'' (with Hooi Ling Soh). \mbox{\textit{33\textsuperscript{rd} Annual Meeting of the Southeast Asian Linguistics Society (SEALS 33)},} National Tsing Hua University, Hsinchu, Taiwan. June 15, 2024. \emph{Presented by co-author.}} 
\talk{``Directed motion in White Hmong: Serial verb constructions as complex PPs.'' \textit{Montreal-Ottawa-Toronto-Hamilton Syntax Workshop (MOTH 2022)}, Universit\'e du Qu\'ebec \`a Montr\'eal. April 23, 2022.}
\talk{``Verb serialization as event-building: Evidence from Hmong.'' \textit{96\textsuperscript{th} Annual Meeting of the Linguistic Society of America (LSA)}, Washington, DC. January 9, 2022.}
\talk{``Nonspecific promises: The Intensional Restitution Effect.'' \textit{Sinn und Bedeutung 26}, University of Cologne. September 10, 2021.}
\talk{``Nonspecific promises: The Intensional Restitution Effect.'' \textit{Toronto-Ottawa-Montreal Semantics Workshop (TOM) 13}, University of Toronto. May 21, 2021.}
%note ad-hoc spacing:
\talk{``Verb serialization as event-building: Evidence from Hmong.'' \textit{Montreal-Ottawa-Toronto-Hamilton Syntax Workshop} \mbox{\textit{(MOTH 2021)}, McMaster University. April 19, 202\rlap{1.}}}
\talk{``Pair-list questions from dependent plurals.'' \textit{22\textsuperscript{nd} Amsterdam Colloquium}, University of Amsterdam. December 19, 2019.}

\subsubsection{Poster Presentations:}
\talk{``Diagnosing Prepositions: Decomposing Path in White Hmong.'' \textit{42\textsuperscript{nd} West Coast Conference on Formal Linguistics (WCCFL 42).} April 13, 2024.}
\talk{``Diagnosing Prepositions: Decomposing Path in White Hmong.'' \textit{Generative Linguistics in the Old World in Asia (GLOW in Asia)}, Chinese University of Hong Kong. March 6, 2024.}
\talk{``Culmination entailments in V and P: Evidence from White Hmong.'' \textit{41\textsuperscript{st} West Coast Conference on Formal Linguistics (WCCFL 41)}, University of California Santa Cruz. May 6, 2023}
\talk{``Focus, too, and conjunction, too: The syntax and semantics of Japanese \textit{mo}-coordination.'' \textit{Minnesota Undergraduate Linguistics Symposium}, St.\ Olaf College. April 13, 2013.}

%%% TEACHING %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Teaching}

\subsection{Courses Taught}
\cvline{Fall 2024}{%
	Language Awareness for ESL Teachers (LIN1130)\\
	Département de linguistique, Université du Québec à Montréal}
\cvline{Winter 2023}{%
	Languages of the World (LING 315)\\
	Department of Linguistics, McGill University}
\cvline{Winter 2021}{%
	Meaning in Language (LING 260)\\
	Department of Linguistics, McGill University}
	
\subsection{Teaching Assistantships}
\cvline{Fall 2021}{%
	Phonetics (LING 330)\\
	Instructor: Connie Ting\\
	Department of Linguistics, McGill University}
\cvline{Fall 2020}{%
	Meaning in Language (LING 260)\\
	Instructor: Bernhard Schwarz\\
	Department of Linguistics, McGill University}
\cvline{Winter 2020}{%
	Phonetics (LING 330)\\
	Instructor: Francisco Torreira\\
	Department of Linguistics, McGill University}
\cvline{Fall 2019}{%
	Phonetics (LING 330)\\
	Instructor: Meghan Clayards\\
	Department of Linguistics, McGill University}
\cvline{Fall 2012}{%
	Introduction to Linguistics (LING 110)\\
	Instructor: Cherlon Ussery\\
	Linguistics Department, Carleton College}

\subsection{Grading}
\cvline{Fall 2020}{% Was this actually winter 2021? 
	Structure of a Specific Language - German (LING 410)\\
	Instructor: Bernhard Schwarz\par
	Department of Linguistics, McGill University}

%%% AWARDS, GRANTS, & FELLOWSHIPS %%%%%%%%%%%%%%%%%%
\section{Awards}

\cvline{2023--2024}{\hang Graduate Research Enhancement and Travel Award, McGill University Faculty of Arts, \$640 CAD\par \hang Graduate Student Travel Award, Centre for Research on Brain, Language and Music, \$700 CAD}
\cvline{2022--2023}{Graduate Excellence Fellowship, McGill University, \$20,000.\\McGill Linguistics Department Travel Fund, \$1,000 CAD}
\cvline{2021--2022}{Graduate Excellence Award, McGill University, \$15,000 CAD.\par \hang Graduate Research Enhancement and Travel Award, McGill University Faculty of Arts, \$141 CAD}
\cvline{2020--2021}{\hang Cremona Memorial Fellowship, McGill University, \$10,000 CAD\par \hang Linguistics Department Nominee, Arts Graduate Student Teaching Award, McGill University.}
\cvline{2019--2020}{Graduate Excellence Award, McGill University, \$1,000 CAD}
\cvline{2018--2019}{Graduate Excellence Award, McGill University, \$15,000 CAD}

% FORMAT: Granting Agency. Grant Name, Institute, \textit{Grant Title} (Grant Number), \$Amount. (Co-investigator(s): Names.)

%%% SERVICE AND COMMUNITY %%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Service \& Community}

\subsection{Department Organizing}
%Note ad-hoc spacing: 
\cvline{\scalebox{.97}[1.00]{Sep.\,2019--Aug.\,2021}}{Editor, \textit{McLing} Newsletter\\McGill University Linguistics Department}
\cvline{Summer 2021}{Organizer, Event Structure Reading Group\\McGill University Linguistics Department}
\cvline{Spring 2021}{Co-organizer, Accepted Students Open House\\McGill University Linguistics Department}
\cvline{Spring 2020}{Co-organizer, Accepted Students Open House\\McGill University Linguistics Department}

\subsection{Conference Organizing}
\cvline{Spring 2023}{Workshop on Structure and Constituency in Languages of the Americas (WSCLA) 2023}

\subsection{Reading and Research Groups}

\cvline{Mar.\ 2022--Present}{University of Minnesota Community-Engaged Hmong Linguistic\rlap{s}\\Research and Reading Group}
\cvline{Sep.\ 2020--Present}{Montreal Underdocumented Languages Linguistics Lab %(MULL-Lab)
}
\cvline{Sep.\ 2018--Present}{McGill Syntax/Semantics Reading Group}
\cvline{Summer 2021}{McGill Event Structure Reading Group}

\subsection{Professional Organizations}
\cvline{Oct.\ 2024--Present}{Linguistic Society of America (LSA)}
\cvline{Oct.\ 2024--Present}{Canadian Linguistic Association (CLA)}
\cvline{Sep.\ 2024--Present}{Generative Linguistics in the Old World (GLOW)}
\cvline{Jun.\ 2023--Present}{Hmong Studies Consortium}
%\cvline{}{Linguistic Society of America}
%\cvline{}{Canadian Linguistic Association}

\subsection{Outreach}
%\cvline{Sep.\2021--Present}{Host: `Hmong Linguistics Resources' web page and annotated bibliography\\ https://williamjohnston.github.io/hmong_linguistics}
\cvline{Spring 2023}{Panel discussion:\,``Ask a Grad Student''\\Society of Linguistics Undergrads at McGill}
\cvline{Spring 2022}{Panel discussion:\,``Ask a Grad Student''\\Society of Linguistics Undergrads at McGill}
%Note ad-hoc spacing: 
\cvline{Winter 2015}{Panel discussion:\,``What paths will a linguistics major take you o\rlap{n?''}\\Carleton College Linguistics Department}

\subsection{Reviewing}
\paragraph{Conference Abstracts:} Annual Conference on African Linguistics (ACAL)
\paragraph{Conference Proceedings:} Toronto--Montreal Bantu Colloquium (Ba-TOM)

%%% NON-DEGREE COURSEWORK %%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Non-degree Coursework}
\cvline{Sep.--Nov.\ 2020}{Hmong Language Workshop\\Southeast Asian Diaspora Project, Minneapolis MN}
\cvline{Summer 2013}{Denver Publishing Institute, University of Denver}

%%% PREVIOUS PROFESSIONAL EXPERIENCE %%%%%%%%%%%%%%%
\section{Previous Professional Experience}
\cvline{Jan.\ 2014--Jul.\ 2018}{Financial Advisor\\Morgan Stanley Wealth Management, Minneapolis MN}

%%% REFERENCES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
